\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[spanish,mexico]{babel}
\usepackage{array,booktabs} 
\usepackage[table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{color}
\usepackage{multicol}
\usepackage{ragged2e}
\usepackage{verbatim}
\usepackage[margin=2.5cm,footskip=0.25in]{geometry}
\usepackage{graphicx} % figuras
\usepackage{subfigure} % subfiguras

\oddsidemargin = 0 cm
\textwidth = 17 cm
\topmargin = -2 cm
\textheight = 26 cm  

\usepackage[spanish]{babel}



\title{Proyecto}
\usepackage[hidelinks]{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=red,
    filecolor=Maroon,      
    urlcolor=OliveGreen,
    citecolor = Maroon
}


\begin{document}

\input{Portada}
\tableofcontents
\newpage

\section{Resumen}
\input{Secciones/Resumen}

\section{Introducción a la base}
\input{Secciones/Introducción a la base}

\newpage

\section{Análisis Descriptivo.}
\input{Secciones/Descriptiva}


\section{Métodos de descomposición}
\input{Secciones/Metodos de descomposicion}


\section{Ajuste serie de Tiempo}
\input{Secciones/Ajuste serie de Tiempo}


\section{Supuestos}
\input{Secciones/Supuestos}

\section{Pronósticos y Conclusiones}
\input{Secciones/Pronosticos}


\begin{thebibliography}{X }
\bibitem{Garch}Bauwens, L., Laurent, S., $\&$ Rombouts, J. V. (2006). Multivariate GARCH models: a survey. Journal of applied econometrics, 21(1), 79-109.

\bibitem{Lundbergh} Lundbergh, S., $\&$ Teräsvirta, T. (2002). Evaluating GARCH models. Journal of Econometrics, 110(2), 417-435.

\bibitem{Francq}Francq, C., $\&$ Zakoian, J. M. (2019). GARCH models: structure, statistical inference and financial applications. John Wiley $\&$ Sons.

\bibitem{Silvennoinen}Silvennoinen, A., $\&$ Teräsvirta, T. (2009). Multivariate GARCH models. In Handbook of financial time series (pp. 201-229). Springer, Berlin, Heidelberg.

\bibitem{Teräsvirta}Teräsvirta, T. (2009). An introduction to univariate GARCH models. In Handbook of financial time series (pp. 17-42). Springer, Berlin, Heidelberg.
\bibitem{Engle}Engle, R. (2001). GARCH 101: The use of ARCH/GARCH models in applied econometrics. Journal of economic perspectives, 15(4), 157-168.

\end{thebibliography}
\end{document}
